Supporting Information

### 2018-03-14 SupportingInformation.Rmd
minor changes

>>>>

<!--do a TL analysis on the data just created-->
```{r tl_analysis, echo=F, cache=T, cache.extra=list(mtime("TaylorsLawTools.R"),seed,mtime("copsurrognd.R"))}
source("TaylorsLawTools.R")

#We are only doing spatial taylor's law because we know a priori temporal
#won't give anything interesting for the surrogates we use

kend.stats.res<-list()
kend.points.res<-list()
spea.stats.res<-list()
spea.points.res<-list()
for (counter in 1:length(kend.surrog))
{
  ks<-kend.surrog[[counter]]
  ss<-spea.surrog[[counter]]
  kend.stats.res[[counter]]<-matrix(NA,5,numdat)
  spea.stats.res[[counter]]<-matrix(NA,5,numdat)
  kend.points.res[[counter]]<-array(NA,c(N,2,numdat))
  spea.points.res[[counter]]<-array(NA,c(N,2,numdat))
  for (sc in 1:numdat)
  {
    khold<-tl_stats(ks[,,sc])
    kend.stats.res[[counter]][,sc]<-khold$s.stats #spatial TL only
    rownames(kend.stats.res[[counter]])<-names(khold$s.stats)
    kend.points.res[[counter]][,,sc]<-as.matrix(khold$s.points)

    shold<-tl_stats(ss[,,sc])
    spea.stats.res[[counter]][,sc]<-shold$s.stats #spatial TL only
    rownames(spea.stats.res[[counter]])<-names(shold$s.stats)
    spea.points.res[[counter]][,,sc]<-as.matrix(shold$s.points)
  }
}
names(kend.stats.res)<-names(kend.surrog)
names(kend.points.res)<-names(kend.surrog)
names(spea.stats.res)<-names(spea.surrog)
names(spea.points.res)<-names(spea.surrog)

#DAN: now you want to compare whether tl held, and the slope (statistically and visually)
#across the different elements of kend.XX.res and spea.XX.res. See drawing of a figure layout on desk.
